\section{Results of prior-form DWBA calculations}
In a transfer reaction A(d,p)B, the transfer T-matrix has a prior-form formula \cite{thompson2009nuclear}
\begin{equation}\label{eq:priorexact}
T_{prior}=\langle\Psi_2^{(-)}(\vec{r}_2,\vec{R}_2)\left|V_{nA}(r_n)+U_{pA}(r_p)-U_{dA}(R_1)\right|\phi_{np}\chi_{dA}\rangle,
\end{equation}
where $\phi_{np}$ and $\chi_{dA}$ are bound states wave-functions, $\vec{r}_n=\vec{r}_p+\vec{r}_1$, 
and $U_{dA}(R_1)$ is the auxiliary potential we choose. 
Under first-order DWBA, it becomes
\begin{equation}\label{tprior}
T_{prior}^{DWBA}=\langle\phi_{nA}\chi_{pB}^{(-)}\left|V_{nA}(r_n)+U_{pA}(r_p)-U_{dA}(R_1)\right|\phi_{np}\chi_{dA}\rangle,
\end{equation}
\par
The differential cross sections of $^{12}$C(d, p)$^{13}$C calculated in both post and prior forms are given in Fig. ??. 
First-order DWBA with finite-range interactions and full complex remnant is used in both calculations. 
The convergence of calculation in prior form is checked in the same way as we discussed in Sec. \ref{sec:post}. 
Variables $rnl$ and $centre$ are chosen based on FRESCO's recommendations. 
As shown in Fig. ??, the results from post- and prior-form calculations have similar trends and are not far from each other. 
If we calculate without any approximation (Eq. \ref{eq:postexact} and \ref{eq:priorexact}), 
the same results should be obtained from both forms. 
But if only first-order DWBA is considered, we expect that small differences between the two results appear, 
which can be seen in Fig. ??. 
\par
It is worth mentioning that the recommended $rnl$, which represents the non-local range, is larger in prior form (??) than that in post form (??). 
In post form (Eq. \ref{tpost}) $U_{pA}(r_p)$ and $U_{pB}(R_2)$ are close to each other as nuclei A and B are very similar. 
Thus, the operator in Eq. \ref{tpost} is approximately $V_{np}(r_1)$, which has a very short range. 
However, in prior form (Eq. \ref{tprior}) $U_{pA}(r_p)$ and $U_{dA}(R_1)$ cannot cancel each other as the elastic scatterings of deuteron on A and proton on A are very different. 
Thus, the operator in Eq. \ref{tprior} has a longer range which comes from optical potentials $U_{pA}(r_p)$ and $U_{dA}(R_1)$. 
A larger $rnl$ in prior-form calculation also leads to a longer runtime. 